---
title: "Homework 7"
author: "Kunaal Raghav"
format: pdf
editor: visual
---

## Package Download

The following r chunk includes the packages we will use for homework assignment

```{r}
library(ISLR2)
library(car)
library(boot)
library(glmnet)
```

## College Applications

Prior to addressing any of the homework assignments, I will be including the training/testing split that the homework requires

```{r}
data("College")

my.college <- College[-484, ] 

my.college <- College[College$Apps <=16000, ] 

train.pct <- 0.78

set.seed(2025)

Z <- sample(nrow(my.college), floor(train.pct*nrow(my.college)))

college.data <- my.college[Z, ]

holdout.data <- my.college[-Z, ]
```

Part A

```{r}


# Fit full model
fit_full <- lm(Outstate ~ ., data = college.data)

# Compute VIF
vif_values <- vif(fit_full)
vif_values

```

Several of the coefficients, such as Apps, Accept, Enroll, and PHD seem to have high colliniarity

Part B

```{r}

#Respective models

model1 <- glm(Apps ~ Private + Accept + Top10perc + Top25perc +
               F.Undergrad + Outstate + Room.Board + PhD +
               perc.alumni + Expend + Grad.Rate,
              data = college.data, family = gaussian)


model2 <- glm(Apps ~ Private + Accept + Top10perc + Top25perc +
               Outstate + Room.Board + PhD + Expend,
             data = college.data, family = gaussian)



AIC(model1, model2)
BIC(model1, model2)

#Respectiv CV


cv1 <- cv.glm(college.data, model1, K = 10)
cv2 <- cv.glm(college.data, model2, K = 10)


cv1$delta[1]
cv2$delta[1]



```

As we expected (Though it was explained in the homework sheet) Model 1 is the lowest for AIC, while model 2 is lowest for the BIC. With the 10 fold cross validation attempt, model 2 has the lowest predicted MSE

Part C

```{r}

x <- model.matrix(Apps ~ ., data = college.data)[, -1] 

y <- college.data$Apps  

cv.ridge <- cv.glmnet(x, y, alpha = 0)


best.lambda <- cv.ridge$lambda.min
best.lambda

plot(cv.ridge)


mse.ridge <- min(cv.ridge$cvm)
mse.ridge
```

Part D

```{r}
x <- model.matrix(Apps ~ ., college.data)[, -1]
y <- college.data$Apps

cv.lasso <- cv.glmnet(x, y, alpha = 1)

plot(cv.lasso)

best.lambda <- cv.lasso$lambda.min
best.lambda

min_mse <- min(cv.lasso$cvm)
min_mse
```
